Supporting Information: Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-05-08 Ben_Manuscripts/transport/Draft.tex
Minor figure changes

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{array}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{tcolorbox}
\usepackage{multicol}

@@

  % TODO: monomer structure
  Molecular dynamics (MD) simulations can give us mechanistic insights with
  atomistic resolution so that we can provide detailed descriptions of small
  solute transport within LLC membrane nanopores and intelligently design new
  membranes for solute-specific separations. In our previous work, we used MD
  simulations to determine the most likely structure of the hexagonal phase
  formed by the monomer Na-GA3C11, expanding upon the most recent experimental
  characterization.~\cite{coscia_understanding_2018,feng_thin_2016} We developed
  techniques to simulate the hexagonal phase formed by neat monomer as well as
  with varying amounts of water in the pores.

  %BJC4: also edited here to help with the flow.
  In this work, we present studies of the transport mechanisms exhibited by 20
  uncharged polar solutes with varying size, chemical functionality and
  hydrophilic character within the pores of an H\textsubscript{II} phase LLC
  membrane. The pores of the H\textsubscript{II} phase have a similar topology to
  the Q\textsubscript{I} phase but their geomeitry is simpler to model. In future
  studies, we will extend our techniques to the Q\textsubscript{I} phase.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ortho_view.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{top_view.pdf}
  \caption{}
  \end{subfigure}
  %MRS3: include a bit more description in the caption of what the system: This is the figure that provides the orientation to the readers of what they will be thinking about for the rest of the paper.
  %BJC3: gave it another shot
  \caption{The H\textsubscript{II} phase formed by LLC monomers consists of pores
  that are approximately straight (a) and packed hexagonally (b). In both figures,
  water molecules that occupy the pores are colored blue, the hydrophilic head 
  groups of the LLC monomers are colored orange and all else is colored gray. 
  The chemical environment within the nanopores is largely determined by the functionality
  of the head groups. Additionally, there is not a well-defined transition
  point from the aqueous pore region to the alkane-dense, hydrophobic tail region,
  generating further complexity.
  }\label{fig:membrane_rendering}
  \end{figure}

@@

  Based on the geometric criteria proposed by Luzar and Chandler 
  \cite{luzar_effect_1996}, we determined a hydrogen bond to exist if the
  distance between the donor, D, and acceptor, A, atoms is less than 
  3.5 \AA~and the angle formed by D--H$\cdot\cdot\cdot$A is less than 30\degree. Attempts
  to describe a hydrogen bond in the context of molecular simulations has
  yielded a number of definitions with no true consensus 
  \cite{prada-gracia_quest_2013} especially since the geometry of hydrogen
  bonds has some dependence on the system being studied. The definition of
  Luzar and Chandler is easily visualized for trajectories using the 
  \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
  %TODO: reference for VMD
  package which allows us to directly check the validity of identified hydrogen bonds.
  In Section~\ref{S-section:hbond_sensitivity} of the Supporting Information, we
  show that our conclusions are insensitive to this definition within a 
  reasonable range of distances and angles.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of all atoms}\label{fig:total_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_water_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of water}\label{fig:total_water_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of all atoms}\label{fig:total_density_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{total_water_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of water}\label{fig:total_water_density_10wt}
  \end{subfigure}
  \caption{Looking down at the $xy$ plane of the LLC membranes, the lowest density regions
  of both membranes are in the pore center and in the distal tail region, furthest from the pore
  center (a \& c). Water is densest in the low density regions (b \& d).}\label{fig:total_density}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt\% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt\% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt\% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt\% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  %MRS2: should an explicit note of the change of scale from 5% to 10% graph; easiest is in the caption.  Could also note it by some
  %MRS2: some sort of graphical indication on the graph itself.  But definitely need to draw attention to it. 
  %TODO: add indication of scale
  \caption{The MSDs of solutes in the 5 wt\% water system (a) are significantly
  smaller than those of the solutes in the 10 wt\% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the 
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
  }\label{fig:msds}
  \end{figure}

>>>>

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
%\usepackage{array}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
%\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{multicol}
\usepackage{tcolorbox}

@@

  Molecular dynamics (MD) simulations can give us mechanistic insights with
  atomistic resolution so that we can provide detailed descriptions of small
  solute transport within LLC membrane nanopores and intelligently design new
  membranes for solute-specific separations. In our previous work, we used MD
  simulations to determine the most likely structure of the hexagonal phase
  formed by the monomer Na-GA3C11, expanding upon the most recent experimental
  characterization.~\cite{coscia_understanding_2019,feng_thin_2016} We developed
  techniques to simulate the hexagonal phase formed by neat monomer as well as
  with varying amounts of water in the pores.

  %BJC4: also edited here to help with the flow.
  In this work, we present studies of the transport mechanisms exhibited by 20
  uncharged polar solutes with varying size, chemical functionality and
  hydrophilic character within the pores of an H\textsubscript{II} phase LLC
  membrane. The pores of the H\textsubscript{II} phase have a similar topology to
  the Q\textsubscript{I} phase but their geometry is simpler to model. In future
  studies, we will extend our techniques to the Q\textsubscript{I} phase.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \vspace{1.4cm}
  \includegraphics[width=\textwidth]{NaGA3C11.pdf}
  \vspace{1cm}
  \caption{}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{ortho_view.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{top_view.pdf}
  \caption{}
  \end{subfigure}
  %MRS3: include a bit more description in the caption of what the system: This is the figure that provides the orientation to the readers of what they will be thinking about for the rest of the paper.
  %BJC3: gave it another shot
  \caption{The H\textsubscript{II} phase formed by LLC monomer NaGA3C11 (a)
  consists of pores that are approximately straight (b) and packed hexagonally (c).
  In both figures, water molecules that occupy the pores are colored blue, 
  the hydrophilic head groups of the LLC monomers are colored orange and all else is colored gray. 
  The chemical environment within the nanopores is largely determined by the functionality
  of the head groups. Additionally, there is not a well-defined transition
  point from the aqueous pore region to the alkane-dense, hydrophobic tail region,
  generating further complexity.
  }\label{fig:membrane_rendering}
  \end{figure}

@@

  Based on the geometric criteria proposed by Luzar and Chandler 
  \cite{luzar_effect_1996}, we determined a hydrogen bond to exist if the
  distance between the donor, D, and acceptor, A, atoms is less than 
  3.5 \AA~and the angle formed by D--H$\cdot\cdot\cdot$A is less than 30\degree. Attempts
  to describe a hydrogen bond in the context of molecular simulations has
  yielded a number of definitions with no true consensus 
  \cite{prada-gracia_quest_2013} especially since the geometry of hydrogen
  bonds has some dependence on the system being studied. The definition of
  Luzar and Chandler is easily visualized for trajectories using the 
  \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
  package which allows us to directly check the validity of identified hydrogen 
  bonds~\cite{humphrey_VMD:_1996}. In Section~\ref{S-section:hbond_sensitivity} 
  of the Supporting Information, we show that our conclusions are insensitive
  to this definition within a reasonable range of distances and angles.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of all atoms}\label{fig:total_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_water_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of water}\label{fig:total_water_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of all atoms}\label{fig:total_density_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{total_water_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of water}\label{fig:total_water_density_10wt}
  \end{subfigure}
  \caption{Looking down at the $xy$ plane of the cross-linked LLC membranes, the lowest
  density regions of both membranes are in the pore center and in the distal tail region,
  furthest from the pore center (a \& c). Water concentration is highest in regions of
  low monomer density regions (b \& d).}\label{fig:total_density}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt\% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt\% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt\% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt\% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  %MRS2: should an explicit note of the change of scale from 5% to 10% graph; easiest is in the caption.  Could also note it by some
  %MRS2: some sort of graphical indication on the graph itself.  But definitely need to draw attention to it. 
  \caption{The MSDs of solutes in the 5 wt\% water system (a) are significantly
  smaller than those of the solutes in the 10 wt\% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the 
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.
  }\label{fig:msds}
  \end{figure}

### 2019-05-08 Ben_Manuscripts/transport/cover_letter.tex
Minor figure changes

	In this article, we use molecular dynamics (MD) simulations in
        order to observe transport of small solutes in an inverted
        hexagonal (H\textsubscript{II}) phase self-assembled lytropic
        liquid crystal (LLC) polymer membrane. This is one of the
        first, and far the most extensive, uses of molecular dynamics
        to understand the molecular details of transport in such
        chemical complex nanostructured channels. Most importantly, we
        show how such channels can give rise to selective transport
        that is not simply size dependent, but also varies according
        to chemical functionality of the solutes.

@@

		\item Eric Jankowski has experience modeling soft materials using molecular dynamics
		including work done simulating structure factors from simulations, much like
		the techniques we use in our work (Boise State University, 208-426-5681,
		\href{mailto:ericjankowski@boisestate.edu}{ericjankowski@boisestate.edu})

>>>>

	In this article, we use molecular dynamics (MD) simulations in
        order to observe transport of small solutes in an inverted
        hexagonal (H\textsubscript{II}) phase self-assembled lytropic
        liquid crystal (LLC) polymer membrane. This is one of the
        first, and by far the most extensive, uses of molecular dynamics
        to understand the molecular details of solute transport in such
        chemically complex nanostructured channels. Most importantly, we
        show how such channels can give rise to selective transport
        that is not simply size dependent, but also varies according
        to chemical functionality of the solutes.

@@

		\item Mahesh Mahanthappa has experience modeling soft materials using molecular dynamics
		including work on ion transport in various ordered liquid crystalline phases. 
		(University of Minnesota, 612-625-4599,\href{mailto:maheshkm@umn.edu}{maheshkm@umn.edu})
